---
title: "Renewable Energy and Sustainable Infrastructure"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = T)

# author: PRISMS Team
# date: December, 2017
# output:
#   ioslides_presentation: 
#     logo: PRISMS_Logo.png
#     fig_caption: yes
#     keep_md: yes
#     smaller: yes
#     widescreen: yes
```

## Data Description
Data from Canada’s Renewable Power Landscape – Energy Market Analysis 2016 report.

This data include provincial and Canadian total renewable electricity capacities from wind, solar, biomass, hydro and other renewables. Annual data from 2005-2015.

Retrieved from: "http://open.canada.ca/data/en/dataset/7e50d70e-f462-48ea-97f5-6c0bc48cfd14" Contains information licensed under the Open Government Licence – Canada.

Capacity:1233 rows, 5 colomns 
Generation:1849 rows, 5 colomns

## Load Library
```{r message=FALSE}
library(readr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(plotly)
library(knitr)
library(kableExtra)
library(gridExtra)
library(ggmap)
```

## Import Datasets
```{r message=FALSE}
RE_Capacity <- read_csv("Data/Renewable_energy_Capacity.csv")
RE_Generation <- read_csv("Data/Renewable_energy_Generation.csv")
RE_Dictionary <- read_csv("Data/RE_Dictionary.csv")
```

## Tidy Datasets
```{r}
RE_Capacity <- RE_Capacity %>%
  rename(Data_Capacity = Data) %>%
  unite(RSV, Region, Source, Year)

RE_Generation <- RE_Generation %>%
  rename(Data_Generation = Data) %>%
  unite(RSV, Region, Source, Year)

RE_Full <- full_join(RE_Capacity, RE_Generation, by = "RSV") %>%
  separate(RSV, into = c("Region", "Source", "Year"), sep = "_") %>%
  rename(Capacity_MW = Data_Capacity) %>%
  rename(Generation_GWh = Data_Generation) %>%
  select(-Unit.x, -Unit.y)
```


```{r}
RE_Full
```

## Make Graphs

```{r}
#Renewable: biomass, hydro, solar, wind
#Others: Coal, Natural Gas, Nuclear, Oil

p1 <- RE_Full %>%
  filter(Capacity_MW>0)%>%
  filter(Region!="Canada")%>%
  filter(Source == "Renewables") %>%
  mutate(Capacity_MW_1 = Capacity_MW[1])%>%
  mutate(relative_cap = Capacity_MW/Capacity_MW_1) %>%
ggplot(aes(x = Year, y = relative_cap, color = Region)) +
  geom_point() +
  #geom_smooth(se = F, method = "lm") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "Capacity(Megawatts, Renewable)")

table(RE_Full$Source)

temp_df1 <- RE_Full %>%
  filter(Capacity_MW>0)%>%
  filter(Region!="Canada")%>%
  filter(Source == c("Coal", "Natural Gas", "Nuclear", "Oil")) %>%
  group_by(Year, Region) %>%
  summarise(avg_capacity = mean(Capacity_MW)) %>%
  filter(Year == 2005|Year == 2006) %>%
  select(Region, avg_capacity)


df2 <- RE_Full %>%
  filter(Source %in% c("Renewables", "All sources")) %>%
  select(-Capacity_MW) %>%
    filter(Generation_GWh>0)%>%
  tidyr::spread(key = Source, value = Generation_GWh) %>%
  filter(Region!="Canada")%>%
  mutate(ratio = Renewables/`All sources`) 

p2 <- df2 %>%
  ggplot(aes(x = as.numeric(Year), y = ratio, color = Region)) +
  geom_point(alpha = 0.2, size =1) +
  geom_smooth(se = F, method = "lm") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "ratio of produced energy (Ren vs all)") +
  scale_x_continuous(breaks = seq(min(as.numeric(df2$Year)), 
                                  max(as.numeric(df2$Year)), 1))

grid.arrange(p1, p2, ncol=2)


```

```{r}
Can_fc_car <- read.csv("canada_car.csv")
Can_fc_car
Can_fc_car_ <- Can_fc_car %>%
  select(c(3:15)) %>%
  slice(6L) %>% 
  gather(c(1:13), key = "Region", value = "n_cars")
Can_fc_car_
```
```{r}
Can_fc_pop <- read.csv("canada_population.csv")
Can_fc_pop
```
```{r}
Can_fc_area <- read.csv("area_canada.csv")
Can_fc_area
```

```{r}
df3 <- df2 %>%
  group_by(Region) %>%
  summarise(mean_ratio = mean(ratio,na.rm = T)) %>%
  filter(mean_ratio > 0)
df3

Can_join <- df3 %>%
  right_join(Can_fc_car_, by = "Region") %>%
  right_join(Can_fc_pop, by = "Region") %>%
  right_join(Can_fc_area, by = "Region") 
  

Can_join
```
```{r}
ggplot(Can_join, aes(mean_ratio, n_cars, color = Region)) +
  geom_point()
```
```{r}
ggplot(Can_join, aes(mean_ratio,X2016, color = Region)) +
  geom_point()
```
```{r}
ggplot(Can_join, aes(mean_ratio, Area, color = Region)) +
  geom_point()
```


## ggmap Graphs
```{r}
Canada_Map <- read_csv("Data/ca_postal_codes.csv")

Full_withGeo <- full_join(Canada_Map, RE_Full, by = "Region")
     
Canada_ggmap <- get_map(location = 'Canada', zoom = 3, 
                        maptype = "terrain",
                        source = 'google', color = 'bw')
     
     ggmap(Canada_ggmap) +
       geom_polygon(data = Full_withGeo %>% filter(Year == 2015), 
                    mapping = aes(x = Longitude, y = Latitude, 
                              fill = Region, group = Region, alpha = Capacity_MW)) +
       ylim(40, 75)
```

```{r}
#14 regions in total
RE_Full %>%
  group_by(Region) %>%
  summarise(n())
```

```{r}
US_energy <- read.csv("us_energy.csv")
US_energy
```
```{r}
ggplot(US_energy, aes(Non.Hydro.Renewable.as...of.Total.Generation, Renewable.as...of.Total.Generation, color = Abbreviation)) +
  geom_point()
```

```{r}
library(utils)
```
```{r}
world_energy <- read.csv("world_energy.csv")
world_energy
```

Prediction
http://stats.oecd.org/